Data- and Ontology Paper: Quality Ontology for Handicap Parking Spots around Venues in Amsterdam

### 2016-04-23 milestone2/paper/paper.tex
pics and report :)

\begin{abstract}
% The abstract should summarize the contents of the paper and should
% contain at least 70 and at most 150 words. It should be written using the
% \emph{abstract} environment.
We introduce a Linked Dataset integrating three different datasets related to
the city of Amsterdam. We present the details of the dataset and the ontology
that we introduce to cover all the important concepts of those data. Also we
provide a thoughtful analysis of the methodology that we applied and the
evaluation techniques that have been embraced. We enhanced our previous dataset
with a richer ontology and we show how we published our results following the
5-star model for Linked Data.
\end{abstract}

@@

As stated in the previous Milestone, we incorporate other ontologies like \texttt{dbepedia} \footnote{The \texttt{dbepedia} namespace is defined at \url{http://dbpedia.org/ontology/}} for location management, and \texttt{geo} \footnote{The \texttt{geo} namespace is defined at \url{http://www.w3.org/2003/01/geo/wgs84_pos}} for latitude and longitude management. This time, we exploit the usage of dbepedia and make use of the equivalence between dbo:Place and dbo:Location. Further explanation of the benefits of this are explained in the following section.

\section{The Ontology}
%\textit{Systematically describe the ontology and highlight the (interesting) design choices you had to make. Were there things you wanted to represent but couldn't given the limitations on the KR language?\footnote{If you do not encounter any limitations, you should be more ambitious about the model!} How did you work around these limitations? (integrity constraints, additional rules?) Describe how the ontology meets the 5 star model for Linked Vocabulary Use.}
A comparison between the old knowledge graph and the newly created ontology is graphically depicted in Figure \ref{fig:ontology}.

\begin{figure}[h] \centering
	\begin{subfigure}{.5\textwidth} \centering
		\includegraphics[width=.9\textwidth]{img/old_ontology.jpg}
		\label{fig:old_ontology}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth} \centering
		\includegraphics[width=.9\textwidth]{img/ontology.png}
		\label{fig:new_ontology}
	\end{subfigure}
	\caption{Difference between original ontology (left) and updated ontology (right).}
	\label{fig:ontology}
\end{figure}

@@

\subsection{Entities}
The main difference with the previous version of the ontology is that each of the three main classes are now subdivided into more specific subclasses. For example:
\begin{itemize}
	\item \textbf{Events}: Divided into Plays and Exhibitions
	\item \textbf{Venues}: Divided into Theatres and Museums
	\item \textbf{Parking Slots}: Divided into Small, Medium and Large Slots
\end{itemize}
A visualization of the current class hierarchy is given in Figure
\ref{fig:ontology-classes}.

\begin{figure}[h] \centering
	\includegraphics[width=.9\textwidth]{img/ontology-classes.png}
	\caption{Class hierarchy for the current version of the Find A Slot ontology.}
	\label{fig:ontology-classes}
\end{figure}

@@

The last extension of the entities regards the creation of a class for \textit{Borough} with the purpose to link it to our Location entity. As explained before, we use the dbepedia for the management of location. However, dbo:Location does not include Boroughs, a crucial part of the description of a  location in Amsterdam. Thus, we create a subclass called Location, which is equivalent to a dbo:Location with a Borough, to represent the specific case of locations in Amsterdam.

@@

The first extension in the Properties regards restrictions on datatype properties. We have included cardinalities with respect to the real world. An example can be seen at the Event entity where we state that in order for an Event to be an Event, it also needs to have at least one Venue where it will take place.

@@

The last extension of our properties section refers to the addition of the properties \textit{Borough} , \textit{City} and \textit{Country}. The reason behind this is that we want to have restrictions. In order to ensure that a dbo:location has exactly one country we use the equivalent rule : 
\\

@@

\begin{lstlisting}[captionpos=b, title=Class equivalent to Location with the use of our subproperty orough, label=lst:owl, basicstyle=\ttfamily\small,frame=bt]
dbo:Location 
and (dbo:borough exactly 1 Borough)
\end{lstlisting}

\section{The Dataset}
% Describe how you recasted the dataset(s) of the previous assignment to the new
% ontology (perhaps you found other datasets that you want to add). What did it
% take to do this? What metadata have you published alongside the dataset, and how
% did you generate it? (Provenance, VOID, etc.) Describe how your data meeds the 5
% star model for Linked Data.
The three datasets have been converted to a linked data format using the second
version of the ontology in a straightforward way. We create
resources for the newly introduced \texttt{Borough} class. Cities have been
recasted to point to DBpedia resources (as for countries).
Entities of class \texttt{Museum} or \texttt{Theater} are created based on their
original dataset of provenience. An \texttt{Event} is linked to a
\texttt{Venue} via a newly created object property and this allows the reasoning
engine to infer if an \texttt{Event} is a \texttt{Play} or an \texttt{Exhibition}.

Given the quantity of slots available for a \texttt{ParkingSlot}, thanks to the
new ontology, the dataset distinguishes parking slots based their availability
into \texttt{SmallSlot}, \texttt{MediumSlot} and \texttt{LargeSlot}. This
provides a richer classification of parking slots than based on the quantity
property directly. This is something that we get through inference, so it has
not been directly coded into the conversion script.

@@

\section{Evaluation}
For evaluating our ontology we got inspired by the work of Hlomani and Stacey
\cite{hlomani2014approaches} on ontology evaluation and decided to evaluate our
ontology using three major criteria:
\begin{enumerate}
	\item \textbf{Task-based Evaluation}. First of all we perform a task-based evaluation that typically evaluates how effective our ontology is in the context of an application.
	\item \textbf{User-based Evaluation}. We perform a user-based evaluation that evaluates the ontology through user's experiences. Contrary to task-based evaluation, we are not accessing semantic validity and consistency of our ontology but we focus on the subjective information of it.
	\item \textbf{Data-driven evaluation}. In the last part of this section we focus on evaluating our ontology by comparing it, with existing data about the domain it models.
\end{enumerate}

@@

\subsection{User-based Evaluation}
For our user-based evaluation we simply examined our dataset as a \textit{third
user}. The source and the meta data that have been added with the void ontology
provide with important information, not only on each of the three datasets
separately but on the dataset as a whole. \textit{Labels}, \textit{descriptions}
and important \textit{metrics}, such as the total number of triples that exist
in each dataset are only some of the meta-data information that have been added.
However the risk with the specific way of evaluation, is that it is difficult to
establish objective standards as it depends on the different type of users
involved.

\subsection{Data-driven evaluation}
So far our ontology combines knowledge from three different datasets in order to
provide a useful service to the potential users of our application. Compared to
other ontologies in the specific domain of finding parking slots it is clear
that our ontology is quite innovative, since we focus specifically on people
with handicap.

@@

\section{Discussion}
\textit{Here you summarize the preceding sections, describe the lessons learnt and discuss future work.}

>>>>

\begin{abstract}
The abstract should summarize the contents of the paper and should
contain at least 70 and at most 150 words. It should be written using the
\emph{abstract} environment.
\end{abstract}

@@

As stated in the previous Milestone, we incorporate other ontologies like \texttt{DBpedia} \footnote{The \texttt{DBpedia} namespace is defined at \url{http://dbpedia.org/ontology/}} for location management, and \texttt{geo} \footnote{The \texttt{geo} namespace is defined at \url{http://www.w3.org/2003/01/geo/wgs84_pos}} for latitude and longitude management. This time, we exploit the usage of DBpedia and make use of the equivalence between dbo:Place and dbo:Location. Further explanation of the benefits of this are explained in the following section.

\section{The Ontology}
%\textit{Systematically describe the ontology and highlight the (interesting) design choices you had to make. Were there things you wanted to represent but couldn't given the limitations on the KR language?\footnote{If you do not encounter any limitations, you should be more ambitious about the model!} How did you work around these limitations? (integrity constraints, additional rules?) Describe how the ontology meets the 5 star model for Linked Vocabulary Use.}
A comparison between the old knowledge graph (Figure \ref{fig:old_ontology}) and the newly created ontology (Figure \ref{fig:ontology-classes}) is graphically depicted below.

\begin{figure}[h]\centering
	\includegraphics[width=.7\textwidth]{img/old_ontology.jpg}
	\caption{Knowledge graph from Milestone 1.}
	\label{fig:old_ontology}
\end{figure}
\begin{figure}[h] \centering
	\includegraphics[width=.7\textwidth]{img/ontology-classes.png}
	\caption{Class hierarchy for the current version of the Find A Slot ontology.}
	\label{fig:ontology-classes}
\end{figure}

@@

\subsection{Entities}
The main difference with the previous version of the ontology is that each of the three main classes is now subdivided into more specific subclasses. For example:
\begin{itemize}
	\item \textbf{Events}: Divided into Plays and Exhibitions
	\item \textbf{Venues}: Divided into Theatres and Museums
	\item \textbf{Parking Slots}: Divided into Small, Medium and Large Slots
\end{itemize}

@@

The last extension of the entities regards the creation of a class for \textit{Borough} with the purpose of linking it to our Location entity. As explained before, we use the DBpedia ontology for the management of locations. However, dbo:Location does not include Boroughs, a crucial part of the description of a  location in Amsterdam. Thus, we create a subclass called Location, which is equivalent to a dbo:Location with a Borough, to represent the specific case of locations in Amsterdam.

@@

The first extension in the Properties regards restrictions on datatype properties. We have included cardinalities with respect to the real world. An example can be seen at the Event entity where we state that an Event must have at least one Venue where it will take place.

@@

The last extension of our properties section refers to the addition of the properties \textit{Borough} , \textit{City} and \textit{Country}. The reason behind this is that we want to have restrictions. In order to ensure that a dbo:location has exactly one country we use the equivalent rule: \\

@@

\begin{lstlisting}[captionpos=b, title=Class equivalent to Location with the use of our subproperty borough, label=lst:owl, basicstyle=\ttfamily\small,frame=bt]
dbo:Location 
and (dbo:borough exactly 1 Borough)
\end{lstlisting}

\section{The Dataset}
% Describe how you recasted the dataset(s) of the previous assignment to the new
% ontology (perhaps you found other datasets that you want to add). What did it
% take to do this? What metadata have you published alongside the dataset, and how
% did you generate it? (Provenance, VOID, etc.) Describe how your data meeds the 5
% star model for Linked Data.
Once again, the three datasets have been converted to a linked data format, now using the second version of the ontology in a straightforward way. We create resources for the newly introduced \texttt{Borough} class. Cities and countries have been recasted to point to DBpedia resources. Entities of class \texttt{Museum} or \texttt{Theatre} are created based on their original dataset of provenance. An \texttt{Event} is linked to a \texttt{Venue} via a newly created object property and this allows the reasoning engine to infer if an \texttt{Event} is a \texttt{Play} or an \texttt{Exhibition} based on its Venue type.

Given the quantity of slots available for a \texttt{ParkingSlot}, thanks to the new ontology, the dataset distinguishes parking slots based their availability into \texttt{SmallSlot}, \texttt{MediumSlot} and \texttt{LargeSlot}. This provides a richer classification of parking slots than based on the quantity
property directly. It is remarkable that we get this through inference since it has not been directly coded into the conversion script.

@@

\section{Section 7 - Evaluation}
For evaluating our ontology we got inspired by the work of Hlomani and Stacey \cite{hlomani2014approaches} on ontology evaluation and decided to evaluate our ontology using three major criterion:
\begin{enumerate}
	\item \textbf{Task-based Evaluation}. First of all we perform a task-based evaluation that typically evaluates how effective our ontology is in the context of an application.
	\item \textbf{User-based Evaluation}. We perform a user-based evaluation that evaluates the ontology through user's experiences. Contrary to task-based evaluation, we are not accessing semantic validity and consistency of our ontology but we focus on the subjective information of it.
	\item \textbf{Data-driven evaluation}. In the last part of this section we focus on evaluating our ontology by comparing it, with existing data about the domain it models.
\end{enumerate}

@@

\subsection{User-based Evaluation}
For our user-based evaluation we simply examined our dataset as a \textit{third user}. The source and the meta data that have been added with the void ontology provide with important information, no only on each of the three datasets separately but on the dataset as a whole. \textit{Labels}, \textit{descriptions} and important \textit{metrics}, such as the total number of triples that exist in each dataset are only some of the meta-data information that have been added. However the risk with the specific way of evaluation, is that it is difficult to establish objective standards as it depends on the different type of users involved.

\subsection{Data-driven evaluation}
So far our ontology combines knowledge from three different datasets in order to provide a useful service to the potential users of our application. Compared to other ontologies in the specific domain of finding parking slots it is clear that our ontology is quite innovative, since we focus specifically on people with a certain handicap.

@@

\section{Discussion}
\textit{Here you summarize the preceding sections, describe the lessons learnt and discuss future work.}
Ontology may be too specific regarding domains and ranges of Object Properties. For example, if a :Location is not related to a Borough, then we will not recognize it as a :Location entity.
